% Adding required packages for the prologue
\documentclass[a4paper,10pt,twocolumn]{memoir}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{geometry}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{lettrine}
\usepackage{tcolorbox}
\usepackage{framed}
\definecolor{shadecolor}{RGB}{240,240,240}
\newenvironment{magquote}
  {\begin{shaded*}\itshape\small}
  {\end{shaded*}}

% Page geometry consistent with the provided format
\geometry{
  a4paper,
  left=15mm,
  right=15mm,
  top=20mm,
  bottom=15mm,
  columnsep=8mm
}

% Color palette consistent with the provided format
\definecolor{primary}{RGB}{30, 50, 100}
\definecolor{accent}{RGB}{200, 80, 0}
\definecolor{light}{RGB}{245, 245, 248}
\definecolor{dark}{RGB}{40, 40, 45}
\definecolor{gray}{RGB}{120,120,120}

% Typography settings consistent with the provided format
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.7em}
\linespread{1.05}
\frenchspacing

% Header/Footer consistent with the provided format
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\footnotesize\scshape\color{primary}The Aevum}
\fancyhead[R]{\footnotesize\color{primary}July 2025}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{accent}\leaders\hrule height \headrulewidth\hfill}}

\begin{document}

% Prologue page
\begin{center}
\vspace*{1cm}

{\Huge\bfseries\color{primary}Prologue}

\vspace{0.5cm}
\tikz{\draw[accent, line width=1pt] (0,0) -- (8cm,0);}

\vspace{0.5cm}
{\large\scshape\color{dark}Welcome to The Aevum}

\vspace{0.3cm}
\end{center}

\lettrine[lines=3]{I}{n} a world racing toward the future, where ideas spark revolutions and technology reshapes reality, *The Aevum* emerges as a beacon of curiosity and insight. Our name, derived from the Latin for "eternity," reflects our mission: to explore the timeless questions that connect yesterday, today, and always. From the ethical dilemmas of ghostwriting to the boundless potential of quantum computing, from the dopamine-driven pull of digital platforms to the quiet triumphs of robotics, this inaugural issue captures the pulse of innovation and human ambition.

\begin{magquote}
"The future belongs to those who believe in the beauty of their dreams." \\
\hfill --- Eleanor Roosevelt
\end{magquote}

This magazine is a celebration of bold minds---students, thinkers, and creators who dare to ask "what if?" and "why not?" Through their voices, we uncover stories that challenge, inspire, and illuminate. Whether you're a dreamer tinkering with microcontrollers or a skeptic pondering the ethics of AI, *The Aevum* is your space to reflect, learn, and imagine.

As you turn these pages, let curiosity guide you. The silent revolutions of our time---in technology, science, and thought---are already shaping tomorrow. Join us in this journey to understand, question, and create a future that resonates with purpose.

\vspace{0.3cm}
{\small\scshape\color{gray}Produced by NeuroNumb}

\vspace*{\fill}
{\large\itshape\color{dark}To the curious, the courageous, and the creators---welcome to eternity.}

\end{document}
